Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-12-16 R0V0.tex
Addressed comment 9 from introduction

\mypara Let $N>0$ be an integer, for each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
\begin{equation}\label{eq:subsystem}
	\dot{x}_i=f_i(x_i,\breve{x}_i)+b_i(x_i)u_i\;,
\end{equation}
where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}. Using this decomposition, the interconnection of system~\eqref{eq:general system} is described by the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$.

>>>>

\mypara Let $N>0$ be an integer and consider the graph $\mathscr{G}$ defined by the set of vertices $\mathscr{V}=\mathbb{N}_{[1,N]}$ and a set of edges $\mathscr{E}\subset\mathbb{N}_{[1,N]}\times\mathbb{N}_{[1,N]}$. For each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
\begin{equation}\label{eq:subsystem}
	\dot{x}_i=f_i(x_i,\breve{x}_i)+b_i(x_i)u_i\;,
\end{equation}
where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}.
